An Examination of Sport Climbing Competition Format and Scoring System

### 2021-08-04 manuscript/Rmd/draft.Rmd
Change theme

```{r}
library(tidyverse)
library(kableExtra)
theme_set(theme_minimal())
```

@@

```{r, fig.cap = "Kendall's rank correlations - 2018 World Championship, Men's and Women's Qualifications", fig.height=8, fig.width=6.5}
mcor <- mq %>% 
  select(Overall = rank, Speed = speed, Bouldering = bould, Lead = lead) %>% 
  ggpairs(diag = "blank",
          axisLabels = "internal",
          upper = list(continuous = wrap("cor", method = "kendall", stars = FALSE))) +
  theme(panel.grid.major = element_blank()) +
  labs(y = "Men\n")

wcor <- wq %>% 
  select(Overall = rank, Speed = speed, Bouldering = bould, Lead = lead) %>% 
  ggpairs(diag = "blank",
          axisLabels = "internal",
          upper = list(continuous = wrap("cor", method = "kendall", stars = FALSE))) +
  theme(panel.grid.major = element_blank())  +
  labs(y = "Women\n")

>>>>

```{r}
library(tidyverse)
library(kableExtra)
theme_set(theme_bw())
```

@@

```{r, fig.cap = "Kendall's rank correlations - 2018 World Championship, Men's and Women's Qualifications", fig.height=8, fig.width=5}
mcor <- mq %>% 
  select(Overall = rank, Speed = speed, Bouldering = bould, Lead = lead) %>% 
  ggpairs(diag = "blank",
          lower = list(continuous = wrap("points", size = 1)),
          upper = list(continuous = wrap("cor", method = "kendall", stars = FALSE, size = 3))) +
  theme(panel.grid.major = element_blank(),
        axis.text = element_text(size = 6)) +
  labs(y = "Men\n")

wcor <- wq %>% 
  select(Overall = rank, Speed = speed, Bouldering = bould, Lead = lead) %>% 
  ggpairs(diag = "blank",
          lower = list(continuous = wrap("points", size = 1)),
          upper = list(continuous = wrap("cor", method = "kendall", stars = FALSE, size = 3))) +
  theme(panel.grid.major = element_blank(),
        axis.text = element_text(size = 6))  +
  labs(y = "Women\n")
